Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-19 FIE2019-final-TPJHD.tex
A couple of further typos fixed

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations - from national academies, learned societies and even governments -- have been presented and discussed in recent years, with varying levels of impact on policy and practice. This paper address the key questions ``What cybersecurity is taught and what cybersecurity should be taught to the generalist Computer Science undergraduate students?'' , ``Should cybersecurity be taught stand-alone or in an integrated manner to generalist Computer Science students?'' and ''Can accreditation by Professional, Statutory and Regulatory Bodies(PSRBs) enhance the provision of cybersecurity within a bodies jurisdiction?''.

Evaluating how cybersecurity is taught in all aspects of computer science is a  task of considerable size. This is beyond the scope the scope of this paper. Instead a case study based research approach has been adopted to evaluate the evidence of the teaching of cybersecurity within general computer science to undergraduate students. Thus, in the context of widespread international computer science/engineering curriculum reform, %- both in compulsory, as well as post-compulsory education - 
what does this need to embed cybersecurity mean more generally for institutions and educators, and how do we teach this subject?

@@

\subsection{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general Computer Science graduate.
\item The general Computer Science masters graduate.
\item The specialist Computer Science graduate.
\item The specialist Computer Science masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the generalist Computer Science undergraduate students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to generalist Computer Science undergraduate students?
\item[RQ3]Can accreditation by PSRBs enhance the provision of cybersecurity within a bodies jurisdiction?
\end{description}

@@

\section{Conclusions}
As regards the research questions;.
\begin{description}
\item[RQ1] - What cybersecurity is taught and what cybersecurity should be taught to the generalist Computer Science undergraduate students?

The guidelines from both ACM and BCS are good for general education. However, the most important item would seem to be an attitude of caution with respect to both offline (\S\ref{sec:SQL}) and online (\S\ref{sec:Java}) resources. 
\item[RQ2] - Should cybersecurity be taught stand-alone or in an integrated manner to generalist Computer Science undergraduate students?

@@

We have the following specific recommendations.
\begin{enumerate}
\item Database courses should look carefully at the security aspects of the texts they use, and the examples they quote, on the lines of \cite{Drop2019}.
\item Web Programming courses should probably do the same, with emphasis on the avoidance of Cross-Site Scripting, and, for production use, the use of a suitable framework\footnote{Most modern frameworks do, but this is not often discussed when looking at the advantages of frameworks.} that has Cross-Site Request Forgery protection. 
\item A study similar to \cite{Drop2019} is recommended for future work in Web Programming, Agile Development, Android Development and potentially other areas of the curriculum.
\item All computer science courses should emphasise that informal resources should come with a ``security health warning'': see sections \ref{sec:informal} and \ref{sec:Java}. One should probably use the data from \cite{Chenetal2019a}: ``If you pick up a SSL/TLS answer from Stack Overflow, there's a 70\% chance it's insecure''.
\end{enumerate}

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations - from national academies, learned societies and even governments -- have been presented and discussed in recent years, with varying levels of impact on policy and practice. This paper address the key questions ``What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science students?'' , ``Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?'' and ''Can accreditation by Professional, Statutory and Regulatory Bodies(PSRBs) enhance the provision of cybersecurity within a bodies jurisdiction?''.

Evaluating how cybersecurity is taught in all aspects of computer science is a  task of considerable size. This is beyond the scope the scope of this paper. Instead a case study based research approach has been adopted to evaluate the evidence of the teaching of cybersecurity within general computer science to students. Thus, in the context of widespread international computer science/engineering curriculum reform, %- both in compulsory, as well as post-compulsory education - 
what does this need to embed cybersecurity mean more generally for institutions and educators, and how do we teach this subject?

@@

\subsection{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general Computer Science graduate.
\item The generalist Computer Science masters graduate.
\item The specialist Computer Science graduate.
\item The specialist Computer Science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by PSRBs enhance the provision of cybersecurity within a bodies jurisdiction?
\end{description}

@@

\section{Conclusions}
As regards the research questions;.
\begin{description}
\item[RQ1] - What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science students?

The guidelines from both ACM and BCS are good for general education. However, the most important item would seem to be an attitude of caution with respect to both offline (\S\ref{sec:SQL}) and online (\S\ref{sec:Java}) resources. 
\item[RQ2] - Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?

@@

We have the following specific recommendations.
\begin{enumerate}
\item Database courses should look carefully at the security aspects of the texts they use, and the examples they quote, on the lines of \cite{Drop2019}.
\item Web Programming courses should  do the same, with emphasis on the avoidance of Cross-Site Scripting, and, for production use, the use of a suitable framework\footnote{Most modern frameworks do, but this is not often discussed when looking at the advantages of frameworks.} that has Cross-Site Request Forgery protection. 
\item A study similar to \cite{Drop2019} is recommended for future work in Web Programming, Agile Development, Android Development and potentially other areas of the curriculum.
\item All computer science courses should emphasise that informal resources should come with a ``security health warning'': see sections \ref{sec:informal} and \ref{sec:Java}. One should probably use the data from \cite{Chenetal2019a}: ``If you pick up a SSL/TLS answer from Stack Overflow, there's a 70\% chance it's insecure''.
\end{enumerate}
